Spatial phylogenetics of Japanese ferns: Patterns, processes, and implications for conservation

### 2021-09-07 ms/SI.Rmd
Add scalebars to maps
take snapshot

---
title: "Appendix S1: Supporting Information"
mainfont: Roboto-Regular.ttf
fontsize: 11pt
mainfontoptions: 
  - BoldFont=Roboto-Bold.ttf
  - ItalicFont=Roboto-Italic.ttf
  - BoldItalicFont=Roboto-BoldItalic.ttf
output: 
  bookdown::pdf_document2:
    citation_package: default
    toc: no
    number_sections: no
    fig_caption: yes
    keep_tex: no
    latex_engine: xelatex
    pandoc_args: [ "--csl", "apa-6th-edition.csl"]
header-includes: 
  - \usepackage{float} # keep figures from floating away
  - \usepackage{booktabs} # need for kable tables
  - \usepackage{colortbl} # need for kable tables
  - \makeatletter\renewcommand*{\fps@figure}{H}\makeatother # keep figures from floating away
  - \usepackage{fancyhdr} # enable header
  - \pagestyle{fancy}  # enable header
  - \fancypagestyle{plain}{\pagestyle{fancy}} # show header on first page
  - \renewcommand{\headrulewidth}{0pt} # delete line beneath header
  - \fancyhead[RE,RO]{Nitta \textit{et al}. Spatial phy. of Japanese ferns Appendix S1} # add header on right side
  - \fancyhead[LO,LE]{} # suppress automatic section header on left side
  - \cfoot{\thepage} # footer
editor_options: 
  chunk_output_type: console
params:
  doc_type: pdf
# nocite: | 
---

@@

```{r setup-si, include = FALSE, cache = FALSE, eval = TRUE}
# Load packages only used when knitting Rmd
library(kableExtra)
library(scales)
library(ggtree)
library(RColorBrewer)
# Load functions and variables only used when rendering Rmds
source(here::here("R/ms_functions.R"), local = TRUE)
# Set knitr options
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, results = "hide", cache = FALSE)
```

@@

```{r phy-sig-binary, results = "as-is"}
binary_sig_results %>%
  select(trait, D, num_present, num_absent, prob_random, prob_brownian) %>%
  arrange(trait) %>%
  # format for kable/latex
  mutate(trait = str_replace_all(trait, "_", "\\\\_")) %>%
  rename(
    "Trait" = trait,
    `\\textit{N} present` = num_present,
    `\\textit{N} absent` = num_absent,
    `\\textit{D}` = D,
    `\\textit{P}(random)` = prob_random, 
    `\\textit{P}(Brownian)` = prob_brownian
  ) %>%
  kbl(booktabs = TRUE, escape = FALSE, format = "latex") %>%
  kable_styling(latex_options = c("striped", "scale_down", "HOLD_position"))
```

**`r s_table("phy-sig-binary")`**. Phylogenetic signal in quantitative (binary) functional traits of the ferns of Japan. *D*, Fritz and Purvis' *D*; *N* (present), number of times a trait was observed present; *N* (absent), number of times a trait was observed absent; *P*(random), probability of obtaining observed trait distribution given random distribution of traits; *P*(Brownian), probability of obtaining observed trait distribution given random evolution by Brownian Motion. Presence or absence of indusium was originally a binary trait; other traits (margin, shape, texture) are qualitative traits scored in binary format.

@@

a <- plot_env("a", "Area", "lat_area", "km^2")
b <- plot_env("b", "% apomictic taxa", "percent_apo", labels = function(x) scales::percent(x, accuracy = 1))
c <- plot_env("c", "Precipitation", "precip", "mm")
d <- plot_env("d", "Precip. season.", "precip_season" , "")
e <- plot_env("e", "Temperature", "temp", "°C", function(x) x/10)
f <- plot_env("f", "Temp. season.", "temp_season")

@@

b <- ggplot() +
  geom_sf(data = japan, fill = "white", color = "transparent", lwd = coast_lwd) +
  geom_sf(data = biodiv_ferns_spatial, aes(fill = redundancy), color = "transparent") +
  geom_sf(data = japan, fill = "transparent", color = coast_col, lwd = coast_lwd) +
  scale_fill_scico(palette = "lajolla") +
  labs(fill = "Redundancy") +
  annotate(geom="richtext", y = Inf, x = -Inf, label = "<span style='color:black'>**(b)**</span>", hjust = "inward", vjust = "inward", color = "white") + 
  map_theme() +
  theme(
    axis.text.y = element_blank()
  )

@@

```{r endemism-restricted, fig.width = 5, fig.height = 5}
ggplot() +
  geom_sf(data = japan, fill = "white", color = "transparent", lwd = coast_lwd) +
  geom_sf(data = biodiv_ferns_endemic_spatial, aes(fill = endem_type), color = "transparent") +
  geom_sf(data = japan, fill = "transparent", color = coast_col, lwd = coast_lwd) +
  scale_fill_manual(values = canape_cols) +
  map_theme() +
  theme(legend.title = element_blank())
```

@@

a <- plot_genus("a", "Equisetum")
b <- plot_genus("b", "Deparia")
c <- plot_genus("c", "Cyrtomium")
d <- plot_genus("d", "Dryopteris")
e <- plot_genus("e", "Pteris")
f <- plot_genus("f", "Diplazium")

@@

a <- make_protected_plot("a", "Richness", richness_obs_p_upper > 0.95)
b <- make_protected_plot("b", "PD", pd_obs_p_upper > 0.95)
c <- make_protected_plot("c", "FD", fd_obs_p_upper > 0.95)
d <- make_protected_plot("d", "PE", pe_obs_p_upper > 0.95)

@@

a <- make_deer_plot("a", "Richness", richness_obs_p_upper > 0.95)
b <- make_deer_plot("b", "PD", pd_obs_p_upper > 0.95)
c <- make_deer_plot("c", "FD", fd_obs_p_upper > 0.95)
d <- make_deer_plot("d", "PE", pe_obs_p_upper > 0.95)

>>>>

---
title: "Appendix S1: Supporting Tables and Figures"
mainfont: Roboto-Regular.ttf
fontsize: 11pt
mainfontoptions: 
  - BoldFont=Roboto-Bold.ttf
  - ItalicFont=Roboto-Italic.ttf
  - BoldItalicFont=Roboto-BoldItalic.ttf
output: 
  bookdown::pdf_document2:
    citation_package: default
    toc: no
    number_sections: no
    fig_caption: yes
    keep_tex: no
    latex_engine: xelatex
    pandoc_args: [ "--csl", "apa-6th-edition.csl"]
header-includes: 
  - \usepackage{float} # keep figures from floating away
  - \usepackage{booktabs} # need for kable tables
  - \usepackage{colortbl} # need for kable tables
  - \makeatletter\renewcommand*{\fps@figure}{H}\makeatother # keep figures from floating away
  - \usepackage{fancyhdr} # enable header
  - \pagestyle{fancy}  # enable header
  - \fancypagestyle{plain}{\pagestyle{fancy}} # show header on first page
  - \renewcommand{\headrulewidth}{0pt} # delete line beneath header
  - \fancyhead[RE,RO]{Nitta \textit{et al}. Spatial phy. of Japanese ferns Appendix S1} # add header on right side
  - \fancyhead[LO,LE]{} # suppress automatic section header on left side
  - \cfoot{\thepage} # footer
editor_options: 
  chunk_output_type: console
params:
  doc_type: pdf
# nocite: | 
---

@@

```{r setup-si, include = FALSE, cache = FALSE, eval = TRUE}
# Load packages only used when knitting Rmd
library(kableExtra)
library(scales)
library(ggtree)
library(RColorBrewer)
library(ggspatial) # for scalebars on maps

# Load functions and variables only used when rendering Rmds
source(here::here("R/ms_functions.R"), local = TRUE)
# Set knitr options
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, results = "hide", cache = FALSE)
```

@@

```{r phy-sig-binary, results = "as-is"}
binary_sig_results %>%
  select(trait, D, num_present, num_absent, prob_random, prob_brownian) %>%
  arrange(trait) %>%
  # format for kable/latex
  mutate(
    trait = str_replace_all(trait, "_", "\\\\_"),
    D = round(D, 3)) %>%
  rename(
    "Trait" = trait,
    `\\textit{N} present` = num_present,
    `\\textit{N} absent` = num_absent,
    `\\textit{D}` = D,
    `\\textit{P}(random)` = prob_random, 
    `\\textit{P}(Brownian)` = prob_brownian
  ) %>%
  kbl(booktabs = TRUE, escape = FALSE, format = "latex", longtable = TRUE) %>%
  kable_styling(latex_options = c("striped", "scale_down", "HOLD_position", "repeat_header"))
```

**`r s_table("phy-sig-binary")`**. Phylogenetic signal in quantitative (binary) functional traits of the ferns of Japan. *D*, Fritz and Purvis' *D*; *N* (present), number of times a trait was observed present; *N* (absent), number of times a trait was observed absent; *P*(random), probability of obtaining observed trait distribution given random distribution of traits; *P*(Brownian), probability of obtaining observed trait distribution given random evolution by Brownian Motion. Presence or absence of indusium was originally a binary trait; other traits (margin, shape, texture) are qualitative traits scored in binary format. Values of *D* rounded to three decimal places.

@@

a <- plot_env("a", "Area", "lat_area", "km^2")
b <- plot_env("b", "% apomictic taxa", "percent_apo", labels = function(x) scales::percent(x, accuracy = 1))
c <- plot_env("c", "Precipitation", "precip", "mm")
d <- plot_env("d", "Precip. season.", "precip_season" , "")
e <- plot_env("e", "Temperature", "temp", "°C", function(x) x/10)
f <- plot_env("f", "Temp. season.", "temp_season") +
  annotation_scale(location = "tl", width_hint = 0.2, pad_y = unit(0.8, "cm"))

@@

b <- ggplot() +
  geom_sf(data = japan, fill = "white", color = "transparent", lwd = coast_lwd) +
  geom_sf(data = biodiv_ferns_spatial, aes(fill = redundancy), color = "transparent") +
  geom_sf(data = japan, fill = "transparent", color = coast_col, lwd = coast_lwd) +
  scale_fill_scico(palette = "lajolla") +
  labs(fill = "Redundancy") +
  annotate(geom="richtext", y = Inf, x = -Inf, label = "<span style='color:black'>**(b)**</span>", hjust = "inward", vjust = "inward", color = "white") +
  annotation_scale(location = "tl", width_hint = 0.2, pad_y = unit(0.8, "cm")) +
  map_theme() +
  theme(
    axis.text.y = element_blank()
  )

@@

```{r endemism-restricted, fig.width = 5, fig.height = 5}
ggplot() +
  geom_sf(data = japan, fill = "white", color = "transparent", lwd = coast_lwd) +
  geom_sf(data = biodiv_ferns_endemic_spatial, aes(fill = endem_type), color = "transparent") +
  geom_sf(data = japan, fill = "transparent", color = coast_col, lwd = coast_lwd) +
  scale_fill_manual(values = canape_cols) +
  annotation_scale(location = "tl", width_hint = 0.2) +
  map_theme() +
  theme(legend.title = element_blank())
```

@@

a <- plot_genus("a", "Equisetum")
b <- plot_genus("b", "Deparia")
c <- plot_genus("c", "Cyrtomium")
d <- plot_genus("d", "Dryopteris")
e <- plot_genus("e", "Pteris")
f <- plot_genus("f", "Diplazium") +
  annotation_scale(location = "tl", width_hint = 0.2, pad_y = unit(0.8, "cm")) +

@@

a <- make_protected_plot("a", "Richness", richness_obs_p_upper > 0.95)
b <- make_protected_plot("b", "PD", pd_obs_p_upper > 0.95)
c <- make_protected_plot("c", "FD", fd_obs_p_upper > 0.95)
d <- make_protected_plot("d", "PE", pe_obs_p_upper > 0.95) +
  annotation_scale(location = "tl", width_hint = 0.2, pad_y = unit(0.8, "cm"))

@@

a <- make_deer_plot("a", "Richness", richness_obs_p_upper > 0.95)
b <- make_deer_plot("b", "PD", pd_obs_p_upper > 0.95)
c <- make_deer_plot("c", "FD", fd_obs_p_upper > 0.95)
d <- make_deer_plot("d", "PE", pe_obs_p_upper > 0.95) +
  annotation_scale(location = "tl", width_hint = 0.2, pad_y = unit(0.8, "cm"))

### 2021-09-07 ms/manuscript.Rmd
Add scalebars to maps
take snapshot

```{r setup, include = FALSE, cache = FALSE}
# Load libraries used for rendering Rmds
library(flextable)
library(kableExtra)
library(ftExtra)
library(scales)
library(patchwork)
library(RColorBrewer)

@@

**Aim** To characterize multiple facets and drivers of biodiversity and understand how these relate to bioregions and conservation status.

**Location** Japan

**Taxon** Ferns

**Methods** We used data from >`r occ_sum$filtered$n_specimens$value %>% plyr::round_any(1000, f = floor) %>% number(big.mark = ",")` fern specimens in Japan to compile a community dataset of `r nrow(comm_ferns) %>% scales::number(big.mark = ",")` 0.2° grid-cells including `r ncol(comm_ferns)` native, non-hybrid taxa. 
We combined this with a phylogenetic tree and functional trait data to analyze taxonomic, phylogenetic, and functional diversity, and modeled the distribution of biodiversity in response to environmental factors and reproductive mode. 
We conducted categorical analysis of neo- and paleo-endemism to identify areas of significant phylogenetic endemism. 
We used hierarchical clustering of taxonomic and phylogenetic distances to analyze bioregions. 
We compared the overlap of significantly diverse grid-cells with existing conservation zones and range maps of native Japanese deer to assess conservation status and threats.

**Results** Three major patterns in the spatial distribution of biodiversity were observed: that of taxonomic richness, which is highest at mid-latitudes, that of phylogenetic and functional diversity and phylogenetic endemism, which are highest in small southern islands, and that of relative phylogenetic and functional diversity, which are high at both high and low latitudes, and low at mid-latitudes. 
Grid-cells were grouped in to `r maj_cluster_count$phylo_cluster$n %>% english2` (phylogenetic) or `r maj_cluster_count$taxonomic_cluster$n %>% english2` (taxonomic) major bioregions. 
Temperature and apomixis were identified as drivers of patterns of taxonomic and phylogenetic diversity.
Conservation status (% protected area) was generally high for grid-cells with significantly high biodiversity, but the threat due to herbivory by deer varied by biodiversity metric, and was particularly severe for taxonomic richness.

**Main conclusions** The integrative approach used here reveals previously undetected patterns and drivers of biodiversity in the ferns of Japan. 
The different distributions of each diversity type reflect the major bioregions. 
Future conservation efforts should recognize that threats can vary by biodiversity metric and consider multiple multiple metrics when establishing conservation priorities.

<!-- may include title words -->
**Key words:** apomixis, biodiversity, biogeography, CANAPE, conservation, ferns, Japan, phylogenetic diversity.

@@

We tested for phylogenetic signal in continuous traits using two alternative metrics, Blomberg's *K* [@Blomberg2003] and Pagel's lambda [@Pagel1999]. 
*K* describes the ratio between the observed variance in a trait vs. the amount of variance expected under Brownian Motion (BM); lambda is a scaling parameter between 0 and 1 that transforms the phylogeny such that trait values fit those most closely expected under BM. 
Both lambda and *K* = 1 under BM; relatively lower values indicate less signal (overdispersion) and higher values indicate more signal (clustering). 
We measured *K* and lambda using the `r func("phylosig")` function in the R package `r pack("phytools")` [@Revell2012], which also calculates significance based on a randomization test for *K* and a likelihood ratio test for lambda. 
We tested for phylogenetic signal in qualitative (coded as binary) traits using Fritz and Purvis' *D* [@Fritz2010] with the `r func("phylo.d")` function in the R package `r pack("caper")` [@Orme2018], which also assesses significance by comparing the observed value to a null distribution of random values and a simulated distribution of values expected under BM.
These methods for phylogenetic signal cannot use a tree with zero-length polytomies, so we used the original dated tree from treePL.

@@

# Sum the number of traits with D < 0
n_negative_d <-
  binary_sig_results %>%
  mutate(negative_d = ifelse(D <= 0, TRUE, FALSE)) %>%
  pull(negative_d) %>%
  sum
```

All continuous traits showed significant phylogenetic signal, but estimates of signal strength differed between *K* and lambda: all lambda values were > 0.95, indicating evolution by BM; however, values of *K* were < 0.1, indicating less phylogenetic signal than expected under BM (`r s_table("phy-sig")`). 
`r n_negative_d` out of `r nrow(binary_sig_results)` of continuous traits (coded as binary) showed as much or more phylogenetic signal as expected under BM (*D* =< 0); others had *D* > 0 (`r s_table("phy-sig-binary")`).

@@

# Make map
japan_map_plot <- ggplot(japan) + 
  geom_sf(size = 0.25) +
  geom_segment(data = japan_lines, aes(x = lon, y = lat, xend = lon_end, yend = lat_end, linetype = query)) +
  scale_linetype_manual(values = c("Tsugaru Strait" = "solid", "Tokara Strait" = "longdash")) +
  geom_richtext(
    data = japan_points, 
    aes(x = lon_adj, y = lat_adj, label = label),
    size = 2.5,
    fill = NA, label.color = NA, # remove background and outline
    label.padding = grid::unit(rep(0, 4), "pt") # remove padding)
  ) +
  geom_point(
    data = filter(japan_points, query == "Tokyo"),
    aes(x = lon, y = lat)
  ) +
  map_theme() +
  theme(legend.position = "none")
```

@@

```{r raw-diversity-make}
# Use thinner coast lines for this plot
# it's smaller, so the grey lines appear relatively thicker
coast_lwd_old <- coast_lwd
coast_lwd <- 0.05

# Richness
a <- ggplot() +
  geom_sf(data = japan, fill = "white", color = "transparent", lwd = coast_lwd) +
  geom_sf(data = biodiv_ferns_spatial, aes(fill = richness), color = "transparent") +
  geom_sf(data = japan, fill = "transparent", color = coast_col, lwd = coast_lwd) +
  annotate(geom="richtext", y = Inf, x = -Inf, label = "<span style='color:black'>**(a)** Richness</span>", hjust = "inward", vjust = "inward", color = "white") + 
  labs(fill = "No. taxa") +
  scale_fill_scico(palette = "lajolla") + 
  scale_x_continuous(breaks = c(125, 135, 145)) +
  scale_y_continuous(breaks = c(25, 35, 45)) +
  map_theme()

@@

# Raw FD
c <- ggplot() + 
  geom_sf(data = japan, fill = "white", color = "transparent", lwd = coast_lwd) +
  geom_sf(data = biodiv_ferns_spatial, aes(fill = fd_obs), color = "transparent") +
  geom_sf(data = japan, fill = "transparent", color = coast_col, lwd = coast_lwd) +
  annotate(geom="richtext", y = Inf, x = -Inf, label = "<span style='color:black'>**(c)** FD</span>", hjust = "inward", vjust = "inward", color = "white") + 
  labs(fill = "Relative\nbranch\nlength") +
  scale_fill_scico(palette = "lajolla") + 
  scale_x_continuous(breaks = c(125, 135, 145)) +
  scale_y_continuous(breaks = c(25, 35, 45)) +
  map_theme() +
  theme(axis.text.y = element_blank())

raw_diversity_plot <- a + b + c +
  plot_layout(nrow = 1)

# Reset coastline width
coast_lwd <- coast_lwd_old
```

@@

# RFD
d <- ggplot() +
  geom_sf(data = japan, fill = "white", color = "transparent", lwd = coast_lwd) +
  geom_sf(data = biodiv_ferns_spatial, aes(fill = rfd_signif), color = "transparent") +
  geom_sf(data = japan, fill = "transparent", color = coast_col, lwd = coast_lwd) +
  annotate(geom="richtext", y = Inf, x = -Inf, label = "<span style='color:black'>**(d)** RFD</span>", hjust = "inward", vjust = "inward", color = "white") + 
  labs(fill = "") +
  scale_fill_manual(values = signif_cols) +
  scale_x_continuous(guide = guide_axis(check.overlap = TRUE)) +
  map_theme() +
  theme(
    axis.text.y = element_blank(),
    legend.title = element_blank()
  )

@@

```{r endemism-make}
endemism_plot <- ggplot() + 
  geom_sf(data = japan, fill = "white", color = "transparent", lwd = coast_lwd) +
  geom_sf(data = biodiv_ferns_spatial, aes(fill = endem_type), color = "transparent") +
  geom_sf(data = japan, fill = "transparent", color = coast_col, lwd = coast_lwd) +
  scale_fill_manual(values = canape_cols) +
  map_theme() +
  theme(legend.title = element_blank())
```

@@

# Phylogenetic bioregions
b <- ggplot() +
  geom_sf(data = japan, fill = "white", color = "transparent", lwd = coast_lwd) +
  geom_sf(data = biodiv_ferns_spatial_lumped, aes(fill = phylo_cluster), color = "transparent") +
  geom_sf(data = japan, fill = "transparent", color = coast_col, lwd = coast_lwd) +
  annotate(geom="richtext", y = Inf, x = -Inf, label = "<span style='color:black'>**(b)** Phylogenetic</span>", hjust = "inward", vjust = "inward", color = "white") + 
  labs(fill = "Bioregion") +
  scale_fill_manual(values = bioregion_cols) +
  map_theme() +
  theme(axis.text.y = element_blank())

>>>>

```{r setup, include = FALSE, cache = FALSE}
# Load libraries used for rendering Rmds
library(flextable)
library(kableExtra)
library(ftExtra)
library(scales)
library(patchwork)
library(RColorBrewer)
library(ggspatial) # for scalebars on maps

@@

**Aim:** To characterize multiple facets and drivers of biodiversity and understand how these relate to bioregions and conservation status.

**Location:** Japan

**Taxon:** Ferns

**Methods:** We used data from >`r occ_sum$filtered$n_specimens$value %>% plyr::round_any(1000, f = floor) %>% number(big.mark = ",")` fern specimens in Japan to compile a community dataset of `r nrow(comm_ferns) %>% scales::number(big.mark = ",")` 0.2° grid-cells including `r ncol(comm_ferns)` native, non-hybrid taxa. 
We combined this with a phylogenetic tree and functional trait data to analyze taxonomic, phylogenetic, and functional diversity, and modeled the distribution of biodiversity in response to environmental factors and reproductive mode. 
We conducted categorical analysis of neo- and paleo-endemism to identify areas of significant phylogenetic endemism. 
We used hierarchical clustering of taxonomic and phylogenetic distances to analyze bioregions. 
We compared the overlap of significantly diverse grid-cells with existing conservation zones and range maps of native Japanese deer to assess conservation status and threats.

**Results:** Three major patterns in the spatial distribution of biodiversity were observed: that of taxonomic richness, which is highest at mid-latitudes, that of phylogenetic and functional diversity and phylogenetic endemism, which are highest in small southern islands, and that of relative phylogenetic and functional diversity, which are high at both high and low latitudes, and low at mid-latitudes. 
Grid-cells were grouped in to `r maj_cluster_count$phylo_cluster$n %>% english2` (phylogenetic) or `r maj_cluster_count$taxonomic_cluster$n %>% english2` (taxonomic) major bioregions. 
Temperature and apomixis were identified as drivers of patterns of taxonomic and phylogenetic diversity.
Conservation status (% protected area) was generally high for grid-cells with significantly high biodiversity, but the threat due to herbivory by deer varied by biodiversity metric, and was particularly severe for taxonomic richness.

**Main conclusions:** The integrative approach used here reveals previously undetected patterns and drivers of biodiversity in the ferns of Japan. 
The different distributions of each diversity type reflect the major bioregions. 
Future conservation efforts should recognize that threats can vary by biodiversity metric and consider multiple multiple metrics when establishing conservation priorities.

<!-- may include title words -->
**Keywords:** apomixis, biodiversity, biogeography, CANAPE, conservation, ferns, Japan, phylogenetic diversity.

@@

We tested for phylogenetic signal in continuous traits using two alternative metrics, Blomberg's *K* [@Blomberg2003] and Pagel's lambda [@Pagel1999]. 
*K* describes the ratio between the observed variance in a trait vs. the amount of variance expected under Brownian Motion (BM); lambda is a scaling parameter between 0 and 1 that transforms the phylogeny such that trait values fit those most closely expected under BM. 
Both lambda and *K* = 1 under BM; relatively lower values indicate less signal (overdispersion) and higher values indicate more signal (clustering). 
We measured *K* and lambda using the `r func("phylosig")` function in the R package `r pack("phytools")` [@Revell2012], which also calculates significance based on a randomization test for *K* and a likelihood ratio test for lambda. 
We tested for phylogenetic signal in qualitative (coded as binary) traits using Fritz and Purvis' *D* [@Fritz2010] with the `r func("phylo.d")` function in the R package `r pack("caper")` [@Orme2018], which also assesses significance by comparing the observed value to a null distribution of random values and a simulated distribution of values expected under BM.
Values of *D* range from 0 under Brownian motion to 1 under random evolution, but can exceed this range in cases of extreme clumping or overdispersion, respectively.
These methods for phylogenetic signal cannot use a tree with zero-length polytomies, so we used the original dated tree from treePL.

@@

# Sum the number of traits with D <= 0.5 and not random
n_d_signif <-
  binary_sig_results %>%
  filter(prob_random < 0.05, D <= 0.5) %>%
  pull(trait) %>%
  n_distinct()
```

All continuous traits showed significant phylogenetic signal, but estimates of signal strength differed between *K* and lambda: all lambda values were > 0.95, indicating evolution by BM; however, values of *K* were < 0.1, indicating less phylogenetic signal than expected under BM (`r s_table("phy-sig")`). 
`r n_d_signif` out of `r nrow(binary_sig_results)` of qualitative traits (coded as binary) showed evidence of phylogenetic signal (*D* ≤ 0.5, significantly different from random) (`r s_table("phy-sig-binary")`).

@@

# Make map
japan_map_plot <- ggplot(japan) + 
  geom_sf(size = 0.25) +
  geom_segment(data = japan_lines, aes(x = lon, y = lat, xend = lon_end, yend = lat_end, linetype = query)) +
  scale_linetype_manual(values = c("Tsugaru Strait" = "solid", "Tokara Strait" = "longdash")) +
  geom_richtext(
    data = japan_points, 
    aes(x = lon_adj, y = lat_adj, label = label),
    size = 2.5,
    fill = NA, label.color = NA, # remove background and outline
    label.padding = grid::unit(rep(0, 4), "pt") # remove padding)
  ) +
  geom_point(
    data = filter(japan_points, query == "Tokyo"),
    aes(x = lon, y = lat)
  ) +
  annotation_scale(location = "br", width_hint = 0.2) +
  map_theme() +
  theme(legend.position = "none")
```

@@

```{r raw-diversity-make}
# Richness
a <- ggplot() +
  geom_sf(data = japan, fill = "white", color = "transparent", lwd = coast_lwd) +
  geom_sf(data = biodiv_ferns_spatial, aes(fill = richness), color = "transparent") +
  geom_sf(data = japan, fill = "transparent", color = coast_col, lwd = coast_lwd) +
  annotate(geom="richtext", y = Inf, x = -Inf, label = "<span style='color:black'>**(a)** Richness</span>", hjust = "inward", vjust = "inward", color = "white") + 
  labs(fill = "No. taxa") +
  scale_fill_scico(palette = "lajolla") + 
  scale_x_continuous(breaks = c(125, 135, 145)) +
  scale_y_continuous(breaks = c(25, 35, 45)) +
  map_theme()

@@

# Raw FD
c <- ggplot() + 
  geom_sf(data = japan, fill = "white", color = "transparent", lwd = coast_lwd) +
  geom_sf(data = biodiv_ferns_spatial, aes(fill = fd_obs), color = "transparent") +
  geom_sf(data = japan, fill = "transparent", color = coast_col, lwd = coast_lwd) +
  annotate(geom="richtext", y = Inf, x = -Inf, label = "<span style='color:black'>**(c)** FD</span>", hjust = "inward", vjust = "inward", color = "white") + 
  labs(fill = "Relative\nbranch\nlength") +
  scale_fill_scico(palette = "lajolla") + 
  scale_x_continuous(breaks = c(125, 135, 145)) +
  scale_y_continuous(breaks = c(25, 35, 45)) +
  annotation_scale(location = "tl", width_hint = 0.2, pad_y = unit(0.8, "cm")) +
  map_theme() +
  theme(axis.text.y = element_blank())

raw_diversity_plot <- a + b + c +
  plot_layout(nrow = 1)
```

@@

# RFD
d <- ggplot() +
  geom_sf(data = japan, fill = "white", color = "transparent", lwd = coast_lwd) +
  geom_sf(data = biodiv_ferns_spatial, aes(fill = rfd_signif), color = "transparent") +
  geom_sf(data = japan, fill = "transparent", color = coast_col, lwd = coast_lwd) +
  annotate(geom="richtext", y = Inf, x = -Inf, label = "<span style='color:black'>**(d)** RFD</span>", hjust = "inward", vjust = "inward", color = "white") + 
  labs(fill = "") +
  scale_fill_manual(values = signif_cols) +
  scale_x_continuous(guide = guide_axis(check.overlap = TRUE)) +
  annotation_scale(location = "br", width_hint = 0.2) +
  map_theme() +
  theme(
    axis.text.y = element_blank(),
    legend.title = element_blank()
  )

@@

```{r endemism-make}
endemism_plot <- ggplot() + 
  geom_sf(data = japan, fill = "white", color = "transparent", lwd = coast_lwd) +
  geom_sf(data = biodiv_ferns_spatial, aes(fill = endem_type), color = "transparent") +
  geom_sf(data = japan, fill = "transparent", color = coast_col, lwd = coast_lwd) +
  scale_fill_manual(values = canape_cols) +
  annotation_scale(location = "br", width_hint = 0.2) +
  map_theme() +
  theme(legend.title = element_blank())
```

@@

# Phylogenetic bioregions
b <- ggplot() +
  geom_sf(data = japan, fill = "white", color = "transparent", lwd = coast_lwd) +
  geom_sf(data = biodiv_ferns_spatial_lumped, aes(fill = phylo_cluster), color = "transparent") +
  geom_sf(data = japan, fill = "transparent", color = coast_col, lwd = coast_lwd) +
  annotate(geom="richtext", y = Inf, x = -Inf, label = "<span style='color:black'>**(b)** Phylogenetic</span>", hjust = "inward", vjust = "inward", color = "white") + 
  labs(fill = "Bioregion") +
  scale_fill_manual(values = bioregion_cols) +
  annotation_scale(location = "br", width_hint = 0.2) +
  map_theme() +
  theme(axis.text.y = element_blank())
